%-------------------------
% Resume in LateX
% Author : Catherine Gilbert
% License : MIT
%------------------------

\documentclass[11pt]{article} % fontsize 10pt/11pt/12pt

\usepackage[margin=1in, letterpaper]{geometry}
\setcounter{secnumdepth}{0} % remove section numbering
\usepackage{titlesec}
% remove vertical spacing above and below
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,left=0pt .. \parindent}
\pagestyle{empty} % remove page number
\pdfgentounicode=1


\begin{document}
\begin{center}
	\begin{minipage}{0.5\textwidth}
		{\Huge\bfseries
			Catherine Gilbert
		} \\ \medskip
	\end{minipage} \hfill
	\begin{minipage}{0.4\textwidth}
		\raggedleft
		Email: recruiting@cathgilbert.com \\
		Mobile: +1 (418) 313-1402 \\
		Website: https://olaren.dev \\
	\end{minipage}
\end{center}


\section{Experience}
%=================%
\subsection{Desjardins \hfill Lévis/Montréal, Qc}
\subsubsection{Analyst-Developer \hfill 2021 -- Current}
\begin{itemize}
	\item Optimized page loading time by up to 750\%
	\item Rewrite of core features in a modern and resilient microservice architecture
	\item Automating visual non-regression tests to reduce QA workload by 20\%
	\item Encryption of confidential data with no impact on service availability
\end{itemize}

\subsection{N'Ware Technologies \hfill Saint-Georges, Qc}
\subsubsection{Intern Developer \hfill Été 2020}
\begin{itemize}
	\item Rewrite and modernization of a warehouse management system
\end{itemize}

\subsection{Staples \hfill Saint-Georges, Qc}
\subsubsection{Computer Technician \hfill 2019-2021}
\begin{itemize}
	\item Diagnosing and fixing various computer problems
\end{itemize}
\subsubsection{Sales Associate \hfill 2017-2019}
\begin{itemize}
	\item Assisting customers with computer, phones, and various
        electronic purchases
\end{itemize}


\section{Education}
%=================%
\subsection{CÉGEP Beauce-Appalaches \hfill Saint-Georges, Qc}
\subsubsection{Computer Science \hfill 2018--2021}
\begin{itemize}
	\item R score: 32.8
	\item Data structures and algorithms
	\item Operating systems
	\item Object-oriented programming
	\item Databases
	\item Networking
\end{itemize}


\section{Skills and interests}
%===========================%
\begin{description}[itemsep=0pt]
	\item[Programming] TypeScript. Java, C\#, Rust, C++, C
	\item[Software] GNU+Linux, Neovim, Git
	\item[Languages] French and English. Oral and written proficiency.
	\item[Interests] Video Games, Japanese culture, privacy and security
\end{description}

\pagebreak{}

\section{Projects}
%===========================%
\begin{itemize}
	\item diffusion: Graphics rendering engine in c99 without third-party libraries.
	\item hudkit-wayland: Wayland overlay to create HUDs with web technologies.
	\item ffxiv-status-contrast \& ffxiv-easy-translate~: Plugins for the
        Final Fantasy XIV game.
	\item uwu-tray: Taskbar icon to UwU-ify text.
	\item dell-fan-control-nvidia: Control servers fan speed based on GPU temperature.
	\item yuri: Reaction images Discord bot.
	\item Homelab / Software self-hosting.
	\item Personal web page.
\end{itemize}


\section{Open Source Contributions}
%===========================%
\begin{itemize}
	\item jellyfin-androidtv: Android TV client for the media server
        software jellyfin.
	\item bevy: ECS game engine written in Rust.
	\item TinyNvidiaUpdateChecker: Manage Nvidia driver updates on windows.
	\item ktor-env-config: Configuring the ktor framework with environment variables.
\end{itemize}

\end{document}
